MacLeish

### 2021-08-06 README.Rmd
Update all stale URL's

# macleish <img src='man/figures/logo.png' align="right" height="139" />

[![R-CMD-check](https://github.com/beanumber/macleish/workflows/R-CMD-check/badge.svg)](https://github.com/beanumber/macleish/actions)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/macleish)](https://cran.r-project.org/package=macleish)

The [Ada and Archibald MacLeish Field Station](http://www.smith.edu/ceeds/macleish.php) is a 260-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation.

@@

This R package allows you to download and process weather data using the [ETL](http://www.github.com/beanumber/etl) framework from the MacLeish Field Station. It also contains shapefiles for contextualizing spatial information.

@@

Weather readings are logged every 10 minutes. Current and historical (dating back to 1/3/2012 for `whately` and 6/27/2014 for `orchard`) meteorological readings are available through the [ETL](http://www.github.com/beanumber/etl) framework. Please see the documentation for that package for more information about how this works.

@@

- [Ada and Archibald MacLeish Field Station](http://www.smith.edu/ceeds/macleish.php)
- **[etl](https://www.github.com/beanumber/etl)**

>>>>

# macleish <img src='man/figures/logo.png' align="right" height="139"/>

[![R-CMD-check](https://github.com/beanumber/macleish/workflows/R-CMD-check/badge.svg)](https://github.com/beanumber/macleish/actions)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/macleish)](https://cran.r-project.org/package=macleish)

The [Ada and Archibald MacLeish Field Station](https://www.smith.edu/about-smith/sustainable-smith/macleish) is a 260-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation.

@@

This R package allows you to download and process weather data using the [ETL](https://www.github.com/beanumber/etl) framework from the MacLeish Field Station. It also contains shapefiles for contextualizing spatial information.

@@

Weather readings are logged every 10 minutes. Current and historical (dating back to 1/3/2012 for `whately` and 6/27/2014 for `orchard`) meteorological readings are available through the [ETL](https://www.github.com/beanumber/etl) framework. Please see the documentation for that package for more information about how this works.

@@

- [Ada and Archibald MacLeish Field Station](https://www.smith.edu/about-smith/sustainable-smith/macleish)
- **[etl](https://www.github.com/beanumber/etl)**
